% Thesis Acknowledgements ------------------------------------------------
%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments
~~~~~This work could not have been completed with out the support of many people, including my coworkers, friends, and family. The massive enthusiasm and commitment to good science of my supervisor, Dr. Peter T. Gallagher, has driven me complete this thesis. His knowledge and experience has consistently led me in the right direction. But his style of supervision gave me the freedom to collaborate and explore many fascinating avenues of this research. He also taught me how to schmooze, network, and advertise (what is the point of doing research if no one hears about it?). This has been paramount to my development as a researcher.

~~~~~For the first half of my time at the College of the Holy and Undivided Trinity of Queen Elizabeth near Dublin, I resided on the 4th floor of the Sami Nasr Institute of Advanced Materials and had some of the best times of my life with the Astrophysics Research Group (ARG!) PhD students. I am thankful that most of the photos have been destroyed. In addition to running amok on the mean streets of Dublin (and beyond), we found time to do some exciting science. The work of the ARG members who have come before and after have always impressed me-- and driven me to do my best. And my appreciation goes to my incredibly smart class mates, Sophie Murray and Peter Byrne (keep on rockin!). 

~~~~~During the second half of my PhD I switched offices to the 3rd floor of the Fitzgerald building. I begin everyday by passing the steely gazes of Hamilton and Schrodinger. I think this, in addition to sharing the office with two hard working postdocs has kept me motivated. Shaun Bloomfield has been instrumental in my understanding of many solar physics topics, and the insight he has provided for each of my projects has improved them immensely. I will never forget drinking tea by the fire in the staff common room on those rainy afternoons, ranting about the government like 75-year-olds. David Perez-Suarez has also been incredibly helpful, especially with regards to making me a better programmer-- and his positivity and absurdist humour has gotten me through many a gray Dublin working day. 

~~~~~I would like to acknowledge the generous tax payers of the ESA member states (Prodex/Proba2, Framework 7/Helio) who have paid for the majority of this PhD, and the TCD school of physics who have paid for the rest. Thanks also go to my external collaborators (especially Tufan, Fraser, and Cis, who accompanied me on those epic ``steam trains" through Switzerland).

~~~~~To Mr. Brian Cooney, for printing the very thesis draft that you are holding in your hand- and to Ms. Deirdre Carroll, for running around town to print shops and offices-- I would not have gotten this thing submitted on time without your help! And to Pietro Zucca for printing the last 30 pages at the last minute, when I finally finished making changes to my last chapter (in the words of Aidan O'Flannagain, "Balls to the wall, huh?")...

~~~~~To my Irish family, thanks for making me feel like I belong in Ireland.
Most importantly, my eternal gratitude goes to my immediate family, Mom, Dad, and Shannon, for their unending love and support, and to my grandmas for always being proud of me.

~~~~~Lastly, to the real reason I was able to stay in Ireland these past years (despite the weather), Ms. Caitlin Cooney. Shine on, you crazy Diamond...
%From that first kiss at a bus stop on Dame St., to these past slightly-less-than 4~years, you dragged me through this ``trauma thing". In that insane moment when I gave up on the thesis and everything else, you wouldn't let me walk away-- that's when I knew for sure that you are the one. 
\end{acknowledgements}
%\end{acknowledgmentslong}
% ------------------------------------------------------------------------